Online Model-Based and Model-Free Reinforcement Learning in Accelerator Operation with Application to FERMI FEL

### 2020-12-04 main.tex
- paper changes

	\author{Simon Hirlaender}
	%\thanks{These two authors contributed equally}
	% \affiliation{University of Malta}
	\affiliation{Univertsity of Salzburg, Salzburg, Austria}
	\author{Niky Bruchon}%, Gianfranco Fenu, Felice Andrea Pellegrino, Erica Salvato}
	\affiliation{University of Trieste, Trieste, IT}
	% \author{Gianluca Valentino}
	% \affiliation{University of Malta, Msida, MT}
	% \author{Marco Lonza, Giulio Gaio}
	% \affiliation{Elettra Sincrotrone Trieste, Trieste, IT}
	% \author{Verena Kain}
	% %\thanks{These two authors contributed equally}
	% \email{verena.kain@cern.ch}

@@

	\subsubsection{Overview of the used algorithms}
	\Cref{tab:overview_algorithms} shows a comparison of the discussed algorithms. Details are provided in the appendix. All algorithms are suitable for many control tasks as common in accelerator operation. Their strength lies in the high sample-efficiency, but they differ in representational power and noise robustness. \\
	In \cref{sec:Experimental results from FERMI RL online tests} the \emph{NAF2},
	\emph{ME-TRPO} and \emph{AE-DYNA} are tested and compared on the real environment.
		\begin{table}[b]%The best place to locate the table environment is directly after its first reference in text
	\caption{\label{tab:overview_algorithms}%
		An overview of the algorithms discussed in this paper.
	}
	\begin{ruledtabular}
		\begin{tabular}{lllll}
			\textrm{Algorithm}&
			\textrm{Class}&
			\textrm{ \begin{tabular}{@{}c@{}}Noise\\robustness\end{tabular}}&
			\textrm{ \begin{tabular}{@{}c@{}}Representational\\power\end{tabular}}&
			\textrm{ \begin{tabular}{@{}c@{}}Sample\\efficiency\end{tabular}}\\
			\colrule
			\emph{NAF} & model-free & low &low &high\\
			\emph{NAF2} & model-free & high &low& high\\
			\emph{ME-TRPO} & model-based & low& high& high\\
			\emph{AE-DYNA} & model-based & high& high& high\\
		\end{tabular}
	\end{ruledtabular}
\end{table}
	\section{Experimental results from FERMI RL online tests}\label{sec:Experimental results from FERMI RL online tests}
	As discussed in the previous sections, several tests were performed on the FERMI FEL.
	The main purpose was to test the newly implemented algorithms on a real system to evaluate its operational feasibility. 
	Because of the tight schedule at FERMI, only a few shifts of several hours could be reserved to carry out these experiments. Since there was a positive outcome, it is evident, that the utilised methods are at an operational level.\\
	The \emph{NAF2} algorithm, the representative for highly sample efficient MFRL algorithms, is discussed first.
	\subsection{MFRL tests}
		\begin{figure}
		\centering
		\includegraphics*[width=0.5\textwidth]{Figures/FERMI_all_experiments_NAF_training_episodes.pdf}
		\caption{The training of the \emph{NAF2} on the FERMI FEL using a single network (dashed) and a double network (solid).}
		\label{fig:NAF_training}
	\end{figure}

>>>>

	\author{Simon Hirlaender}
	%\thanks{These two authors contributed equally}
	% \affiliation{University of Malta}
	\affiliation{Univertsity of Salzburg, Salzburg, Austria}
	\author{Niky Bruchon}%, Gianfranco Fenu, Felice Andrea Pellegrino, Erica Salvato}
	\affiliation{University of Trieste, Trieste, Italy}
	% \author{Gianluca Valentino}
	% \affiliation{University of Malta, Msida, MT}
	% \author{Marco Lonza, Giulio Gaio}
	% \affiliation{Elettra Sincrotrone Trieste, Trieste, IT}
	% \author{Verena Kain}
	% %\thanks{These two authors contributed equally}
	% \email{verena.kain@cern.ch}

@@

	\subsubsection{Overview of the used algorithms}
	\Cref{tab:overview_algorithms} shows a comparison of the discussed algorithms. Details are provided in the appendix. All algorithms are suitable for many control tasks as common in accelerator operation. Their strength lies in the high sample-efficiency, but they differ in representational power and noise robustness. \\
	In \cref{sec:Experimental results from FERMI RL online tests} the \emph{NAF2},
	\emph{ME-TRPO} and \emph{AE-DYNA} are tested and compared on the real environment.
\begin{table}[b]%The best place to locate the table environment is directly after its first reference in text
	\caption{\label{tab:overview_algorithms}%
		An overview of the algorithms discussed in this paper.
	}
	\begin{ruledtabular}
		\begin{tabular}{lllll}
			\textrm{Algorithm}&
			\textrm{Class}&
			\textrm{ \begin{tabular}{@{}c@{}}Noise\\robustness\end{tabular}}&
			\textrm{ \begin{tabular}{@{}c@{}}Represent.\\power\end{tabular}}&
			\textrm{ \begin{tabular}{@{}c@{}}Sample\\efficiency\end{tabular}}\\
			\colrule
			\emph{NAF} & model-free & low &low &high\\
			\emph{NAF2} & model-free & high &low& high\\
			\emph{ME-TRPO} & model-based & low& high& high\\
			\emph{AE-DYNA} & model-based & high& high& high\\
		\end{tabular}
	\end{ruledtabular}
\end{table}
\begin{table}[b]%The best place to locate the table environment is directly after its first reference in text
	\caption{\label{tab:overview_algorithms_results}%
		An overview over the experimental results of the different algorithms.
	}
\begin{ruledtabular}
\begin{tabular}{llrr}
%\toprule
&    &  mean &   std \\
%\midrule
ae\_dyna & cum & -1.44 &  1.10 \\
me\_trpo & cum & -1.95 &  1.76 \\
naf\_double & cum & -0.58 &  0.72 \\
naf\_single & cum & -0.66 &  0.80 \\
ae\_dyna & final &  0.04 &  0.06 \\
me\_trpo & final &  0.01 &  0.04 \\
naf\_double & final & -0.00 &  0.02 \\
naf\_single & final &  0.00 &  0.02 \\
ae\_dyna & nr &  4.28 &  1.26 \\
me\_trpo & nr &  5.46 &  2.32 \\
naf\_double & nr &  2.67 &  1.33 \\
naf\_single & nr &  2.56 &  1.26 \\
\end{tabular}
\end{ruledtabular}
\end{table}

	\section{Experimental results from FERMI RL online tests}\label{sec:Experimental results from FERMI RL online tests}
	As discussed in the previous sections, several tests were performed on the FERMI FEL.
	The main purpose was to test the newly implemented algorithms on a real system to evaluate its operational feasibility. 
	Because of the tight schedule at FERMI, only a few shifts of several hours could be reserved to carry out these experiments. Since there was a positive outcome, it is evident, that the utilised methods are at an operational level.\\
	The \emph{NAF2} algorithm, the representative for highly sample efficient MFRL algorithms, is discussed first.
	\subsection{MFRL tests}
		\begin{figure}
		\centering
		\includegraphics*[width=0.5\textwidth]{Figures/FERMI_all_experiments_NAF_training_episodes.pdf}
		\caption{The training of the \emph{NAF2} on the FERMI FEL using a single network (dashed) and a double network (solid).}
		\label{fig:NAF_training}
	\end{figure}
